Trump Expecting to Win 53% of Popular Vote in 2020 US Presidential Election

### 2020-11-01 outputs/paper/paper.Rmd

## Post-stratification dataset

>>>>

## Post-stratification dataset
The post-stratification dataset was gathered from the American Community Survey (ACS), a project aiming to mitigate issues stemming from the census’ 10-year intervals by providing an annualized version of data like that produced by the decennial census long form. The dataset used in this study is specifically that of the 2018 ACS data. The ACS data can be accessed at the IPUMS website. More details on attaining and cleaning data are found in 01-data_cleaning-post-strat.R in the scripts folder of the git repository.

The target population, much like the census, is essentially anyone who resides in a dwelling in the US. Following this, the sampling frame of the ACS is the Master Address File that is maintained by the US Census Bureau. Created for the 2000 Census, it was originally based on the 1990 Address Control File and the United States Postal Service’s Delivery Sequence File. The maintaining and updating of this file is crucial to the efforts of the ACS and any other body that makes use of it. In addition, the ACS samples 2.5 percent of the population living “Group Quarters”, non-housing units (eg. nursing homes, prisons, college dorms, etc.). In total, the 2018 ACS data contains about 3.2 million observations, sampled from across the country.

Every month, a systemic sample is created for each US county or equivalent, where they are mailed the ACS survey at the start of the month. As of February 2002, the sampling rate of all counties has been 2.5%, except for Houston, Texas, which is sampled at 1% (due to the size of the population). For every site, the sampling is broken into two steps. The first step is sampling 17.5% of the population, which is then subsampled from to achieve that desired percentage. All non-respondents are subsequently contacted by phone for a computer assisted telephone interview one month later. One third of non-respondents that have reached this point are then sampled from to be contacted for a computer assisted personal interview following the previous telephone interview attempt. Beyond this sample (referred to as the National Sample or Supplemental Sample), data was also collected at 31 selected test sites to represent areas with various county population sizes or areas that were difficult to enumerate. The ACS data is weighted in order to ensure reliable and usable estimated regarding the population.

The ACS Questionnaire asks questions regarding every inhabitant in the residence it is sent to. However, the most information is required of “Person 1”, the person whose name the residence is owned in, being bought in, or rented in (or any adult, if none of those labels apply). The ACS questionnaire is extremely like that of the US Census Questionnaire, given that it’s meant to be a substitution for it. It was developed after the Census Bureau was provided with various subjects that other federal agencies justified as important, categorizing each subject as “mandatory”, “required”, or “programmatic”, from which the ACS collected data for both the “mandatory” and “required” subjects. This approach illustrates itself in the questionnaire, as every question is answered by an objective fact, whether it’s a checkbox, a number, or a short answer (such as the person’s major). This allows little ambiguity in how the question must be answered, and makes each response fairly easy, which is a major strength of the questionnaire. However, depending on the number of people in the residence, the survey can be on the longer side (up to 11 pages). Combined with the fact that it is legally mandated that the response is filled out, with a potential fine of up to $5000, respondents may feel the need to rush through or give a fake response to questions they may not know immediately (such as when the residence was built). In addition, in the case that there is not one single person responsible for the residence, like in the case where multiple people are renting a room from one landlord who doesn’t live at the residence, then the data of those who are not “Person 1” is not collected, despite the fact that they are on the same standing in the eyes of the survey. However, no one has been prosecuted for not filling out the survey since 1970 and the case outlined in the second point is relatively rare in the total population, so these weaknesses are fairly minor in the grand scheme of things.

As mentioned above, the variables we used were age (the age of the respondent), state (the state they lived in), gender (what gender they identified as), education (what their highest level of education was), and race/ethnicity of the respondent. However, as the post-stratification data was a different dataset to that of the survey data, we had to transform the post-stratification data to match that, including general cleaning in the sense of converting non-numeric values to numeric, matching up spelling/capitalization of certain responses, and constructing an age_groups variable from the ages given. For more information, please see 01-data_cleaning-post-strat.R in the scripts folder of the github repository.   <-- This section is to be updated accordingly

```{r post-strat graphs}
# Plot Race
perc_race <- cleaned_data %>% count(race_ethnicity) %>% mutate(perc = n/nrow(cleaned_data))
race <- perc_race %>% ggplot(aes(x = race_ethnicity, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Race/Ethnicity of Respondents in 2018 ACS data",
                                                                               x = "Race/Ethnicity", y = "Percentage", subtitle = "Figure X")
race

# Plot Gender
perc_gender <- cleaned_data %>% count(gender) %>% mutate(perc = n/nrow(cleaned_data))
gender <- perc_gender %>% ggplot(aes(x = gender, y = perc)) + geom_bar(stat = "identity") + 
  labs(title = "Gender of Respondents in 2018 ACS data", x = "Gender", y = "Percentage", subtitle = "Figure X")
gender

# Plot education
perc_education <- cleaned_data %>% count(education) %>% mutate(perc = n/nrow(cleaned_data))
perc_education$education <- perc_education$education %>% factor(levels = c("High School or less", "Post Secondary Degree"))
education <- perc_education %>% ggplot(aes(x = education, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Education of Respondents in 2018 ACS data",
                                                                               x = "Education", y = "Percentage", subtitle = "Figure X")
summary(cleaned_data$education)
education

# Explain 88 Olds are shit

# Plot state
perc_state <- cleaned_data %>% count(state) %>% mutate(perc = n/nrow(cleaned_data))
perc_state$state <- perc_state$state %>% factor(levels = sort(as.character.factor(perc_state$state))) 
state <- perc_state %>% ggplot(aes(x = state, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "State of Respondents in 2018 ACS data",
                                                                               x = "State", y = "Percentage", subtitle = "Figure X")
state

# Plot age_group
perc_age_group <- cleaned_data %>% count(age_group) %>% mutate(perc = n/nrow(cleaned_data))
#perc_age_group$age_group <- perc_age_group$age_group %>% factor(levels = sort(as.character.factor(perc_age_group$age_group))) 
age_group <- perc_age_group %>% ggplot(aes(x = age_group, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Age of Respondents in 2018 ACS data",
                                                                               x = "Age Group", y = "Percentage", subtitle = "Figure X")
age_group
```
